---
title: 'NHSD release registers: dataset use'
author: "Lisa Hopcroft"
date: "08/11/2021"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readxl)
library(magrittr)
library(dplyr)
library(stringr)
library(knitr)
library(glue)
library(zoo)
```

# Uses of the Medicines dispensed in Primary Care dataset

The data were obtained from [here](https://nhs-prod.global.ssl.fastly.net/binaries/content/assets/website-assets/services/dars/data-uses-register/datausesregister_november2021.xlsx), from [this landing page](https://digital.nhs.uk/services/data-access-request-service-dars/data-uses-register).
This contains all DSA (data sharing agreements) active from January 2020 to November
2021.

## Last release of data

```{r}


all_releases.data = readxl::read_excel("DataUsesRegister_November2021.xlsx", sheet="DataReleases")

latest_release = all_releases.data %>% pull( `Month File Released`) %>% as.yearmon(dates, format = "%b-%y") %>% max

```

The most recent date for any release of data is `r latest_release`.

## Number of applications

```{r}

this_dataset.name = "Medicines dispensed in Primary Care (NHSBSA data)"

all_datasets.data = readxl::read_excel("DataUsesRegister_November2021.xlsx", sheet="Datasets")

this_dataset.data = all_datasets.data %>% 
    filter( Dataset == this_dataset.name ) %>% 
    mutate( application_number = str_remove( `Reference Number`, "-v.*" ) )

this_dataset.application_numbers = this_dataset.data %>% pull( application_number ) %>% unique

```

There are `r length(this_dataset.application_numbers)` unique applications
requesting access to this dataset (note that different versions of these
applications are counted as one application).

## Organisations and projects

The `r length(this_dataset.application_numbers)` unique applications map to
multiple organisations as individual applications may have cover multiple DSAs
(for different time periods), the leading applicant organisation for that
application may change over time etc.


```{r}

all_agreements.data = readxl::read_excel("DataUsesRegister_November2021.xlsx", sheet="Agreements")

dataset_agreements.data = all_agreements.data %>% 
    mutate( application_number = str_remove( `Reference Number`, "-v.*" ) ) %>% 
    select( -`Reference Number` ) %>% 
    unique() %>% 
    filter( application_number %in% this_dataset.application_numbers ) 

organisation_summary = dataset_agreements.data %>% 
    select( `Applicant Organisation`, `Application Title` ) %>% 
    unique() %>% 
    group_by( `Applicant Organisation` ) %>% 
    summarise( count=n() ) %>% 
    arrange( -count )

num_organisations = dataset_agreements.data %>%
    pull( `Applicant Organisation` ) %>%
    unique() %>% length

```

There are `r num_organisations` organisations who are listed as the lead
applicants for these applications. The number of different projects
(as measured by unique project titles) for each organisation is provided below:

```{r}

knitr::kable( organisation_summary )

```

## Project summary 

More detail about the projects summarised in the table above are provided below:

```{r results = "asis"}

these_organisations = organisation_summary %>%
    pull( `Applicant Organisation`) %>% 
    unique

for ( this_organisation in these_organisations ) {

    project_list = dataset_agreements.data %>% 
        filter( `Applicant Organisation` == this_organisation ) %>% 
        pull( `Application Title` ) %>% 
        unique()

    print( glue("### {this_organisation}\n\n"))
    
    for ( p in 1:length( project_list ) ) {
        print( glue("{p}. {project_list[p]}\n\n") )
    }

} 

```
